Examination of shapes! (homework exam)

### 2016-02-20 geometricAlgorithms/homeworkExam/homeworkExam.tex
improved the algorithm to not be the wrong one

\subsection{Give an algorithm that detrmines an $xy$-silhouette of a conves polyhedron $P$ in O(n) time}
\begin{algorithmic}
	\State Sort all line segment $s \in S$ end points $p$ based on
		$y$ coordinate.
		$p$ should have a reference to its coorisponding point (ie the start
		point has a reference to the end point and vice versa). The resulting
		collection is called $E_{sorted}$
	\For{point$\in E_{sorted}$}
		\State
		\If{begin point} insert in State. On inserted point calculate
		if there is a crossing if so insert in $E_{sorted}$.
		\EndIf
		\If{end point} remove begin point from state.
		\EndIf
		\If{Crossing point} add to result.
		\EndIf
	\EndFor
\end{algorithmic}

\subsection{Why takes this algorithm linear time}
\section{Red and blue lines}
\section{Polygon cut}
\section{Diagonal polygon cut}
\end{empfile}
\end{document}

>>>>

\subsection{Give an algorithm that detrmines an $xy$-silhouette of a conves polyhedron $P$ in O(n) time}
I'm gonna use recursion for this.

%TODO looks to simple\dots
\begin{algorithmic}
	\Function{findxySilhouette}{startVert, currentVert, result}
	\If{startVert is equal to currentVert} \State \Return result \EndIf
	\State
	$nextVert \gets currentVert.incidentEdge.next.origin$
	\State
	\Return findxySilhoeutte(startVert, nextVert, result.append(nextVert))
	\EndFunction
	\Function{findxySilAlgoirthm}{startVert}
	\State \Return
	\Call{findxySilhoeutte}{startVert, startVert.incidentEdge.next.origin, Seq(startVert)}
	\EndFunction
	\State 
\end{algorithmic}

\subsection{Why takes this algorithm linear time}

\section{Red and blue lines}
\section{Polygon cut}
\section{Diagonal polygon cut}
\end{empfile}
\end{document}
